### 2015-10-29 postdoctoral/gamma_functions.tex
some examples of limit computations

  \begin{theorem}
    Let \(M\) be a LOTS with minimum \(0\).
    \(
      Z
        =
      \varprojlim^\star \{M, \nu, L\}
        \cong
      \{-\infty\}\cup (\hat L\setminus\emptyset)\lexTimes M'
    \)
    where \(M'=M\setminus\{0\}\),
    \(\lexTimes\) induces the lexicographic ordering on the product,
    and \(-\infty\) is a least element.
  \end{theorem}

  \begin{proof}
    Let \(\rho(\vect x)=\{a\in L:\vect x(a)>0\}\);
    this is obviously leftwards, and it's closed for all \(\vect x\in Z\).
    Then we give \(Z\) the linear order where \(\vect x<\vect y\) if
    \(\rho(\vect x)\subsetneq\rho(\vect y)\) or both
    \(\rho(\vect x)=\rho(\vect y)\)
    and \(\vect x(l)<\vect y(l)\) for some \(l\in L\).

    Define \(r:Z\to \hat L\lexTimes M\)
    by \(r(\vect 0)=-\infty\) and \(r(\vect x)=\<\rho(\vect x),m\>\) where
    \(\vect x(l)=m>0\) for some \(l\in L\) otherwise.

    We first show that \(r\) is a bijection. Let \(A\) be left-closed
    and \(m\in M'\). Then let \(\vect x_{A,m}\) satisfy \(\vect x_{A,m}(a)=m\)
    for \(a\in A\) and \(\vect x_{A,m}(a)=0\) otherwise and note
    \(\vect x_{A,m}\in Z\), \(r(\vect x_{A,m})=\<A,m\>\). Showing one-to-one
    is similarly trivial.

    Finally let \(\vect 0<\vect x<\vect y\).
    If \(\rho(\vect x)\subsetneq\rho(\vect y)\), then \(r(\vect x)<r(\vect y)\).
    Otherwise \(\rho(\vect x)=\rho(\vect y)\), but \(0<\vect x(l)<\vect y(l)\)
    for some \(l\in L\) and therefore \(r(\vect x)<r(\vect y)\).
  \end{proof}

  This gives us the previous result as a corollary:
  \(
    \varprojlim^\star \{2, \nu, L\}
      \cong
    \{-\infty\}\cup(\hat L\setminus\{\emptyset\})\lexTimes\{1\}
      \cong
    \hat L
  \). Unfortunately, the result is not always compact.

  \begin{example}
    \(
      \varprojlim^\star \{I, \nu, I\}
        \cong
      \{-\infty\}\cup (0,1]\lexTimes(0,1]
    \)
  is not compact.
  \end{example}

  \begin{proof}
    The infinite set \(\{\<1-\frac{1}{2^n},1-\frac{1}{2^n}\>:0<n<\omega\}\)
    is closed discrete.
  \end{proof}

>>>>

  \bigskip

  The ready may verify the following examples:

  \begin{example}
    \(\varprojlim\{2,\gamma,I\}\cong \check L\lexTimes 1\)
  \end{example}
  \begin{example}
    \(\varprojlim\{I,\gamma,I\}\cong I\lexTimes I\)
  \end{example}
  \begin{example}
    \(\varprojlim\{I,\gamma,\omega\}\cong (\omega\lexTimes[0,1))\cup\{\infty\}\)
  \end{example}
  \begin{example}
    \(\varprojlim\{I,\gamma,\omega+1\}\cong \omega+1\lexTimes I\)
  \end{example}
  \begin{example}
    \(\varprojlim\{I,\gamma,-\omega\}\cong \{-\infty\}\cup(-\omega\lexTimes(0,1])\)
  \end{example}
  \begin{example}
    \(\varprojlim\{I,\gamma,I\}\cong I\lexTimes I\)
  \end{example}

  \begin{theorem}
    If \(K,L\) are compact linearly orders, then
    \(\varprojlim\{K,\gamma,L\}\cong L\lexTimes K\).
  \end{theorem}

  \begin{proof}

  \end{proof}
